The transition redshift as a probe of reionization

### 2019-08-12 paper/ms.tex
Add two plots to results section

>>>>

\section{Results} \label{sec:results}
\subsection{The halo field}
We first investigate the dependence of the transition redshift as defined by
the halo field. Fig.~\ref{fig:ztran_vs_k} shows the transition redshift
defined by the 21~cm\,--\,density cross-power spectrum (see
Eq.~\ref{eq:ztran_def}) as a function of $k$. The three models considered in
this work are shown in orange, gray, and teal (\hot{}, \fid{}, and \cold{},
respectively).

Fig.~\ref{fig:ztran_vs_k} shows that \zst{} is only weakly a function of $k$.

\begin{figure}
\includegraphics[width=\columnwidth]{../plots/ztran_vs_k/ztran_vs_k.pdf}
\caption{The transition redshift ($\zst$) as defined by cross-correlating with the
density field (solid lines) and all resolved halos (dashed lines, $M\gtrsim
5\times10^9\,\Msun$), for our three different EoR models (\hot{}, \fid{}, and
\cold{}). We see that \zst{} is only a mild function of $k$ for the three
models, with slightly stronger dependence as the heating of the model
decreases. The most dependence comes in the \cold{} model, where \zst{}
changes by $\sim7\,\%$ from $k=0.1$ to $0.6\,\hoverMpc$. {\bf Some words for
why cold and fid cut off at some k}}
\label{fig:ztran_vs_k}
\end{figure}

\begin{figure}
\includegraphics[width=\columnwidth]{../plots/ztran_vs_Mcut/ztran_vs_Mcut.pdf}
\caption{The transition redshift (\zst) as defined by cross-correlating with the halo field for our three different EoR models (\hot{}, \fid{}, and
\cold{}) as a function of the cut-off mass. The cross-correlation is only made
between the 21~cm field and all halos with masses $M>M_{\text{cut}}$. One can
see that for the \fid{} and \cold{} models, \zst{} is only mildly a function
of $M_{\text{cut}}$ below a certain cut-off mass ($\sim10^{10.5}\,\Msun$ in
both models). In other words, as long as a galaxy survey is deep enough so as
to resolve a sufficient number of galaxies, the \zst{} is not dependent on the
depth of the survey. The \hot{} model shows more dependence, but this may be
due to sampling noise due to the smaller number of such halos at the higher
\zst{} typical for the \hot{} model.}
\end{figure}
